### 2019-09-12 manuscript.tex
Update manuscript.tex

Female genital cutting (FGC), circumcision or mutilation is mostly defined as violating human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly shared position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also foreseen that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in FAC decision\cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

FGC is embodied with multiple perspectives from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} for any negotiation and to reduce possible harmful intervention \cite{Cami15}.  Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}; it can refer to an average outcome or a common practice \cite{MillPrin16}.   Social norms is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15}, provides a crucial venue in negotiating sustainable changes of FGC practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.  Social convention theory, a leading theory (e.g., \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.   FGC was furthered deemed as a form of social capital, a value expected by women for inclusion within their social groups \cite{ShelWand11}. The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.  Social expectation (i.e., what other people do or what other people believe one should do) was strongly correlated with FGC practice \cite{BiccMari15}.  Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.

@@

% education:  \cite{DalaLawo10, IliyAbub12, KandNwak09, KarmKand11, PashPonn16, VanMeek1}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.

>>>>

Female genital cutting (FGC), circumcision or mutilation is mostly defined as violation of human rights \cite{WHO97, WHO08} \cfonly{add and update}.  The commonly position of FGC is about abolishment than intervention of the practice \cite{KhosBane17, Mack96, Toub94, UNIC16, WHO97}.  It is estimated, based on a UNICEF global database \cite{AdnrLesc16, UNIC16} \cfcmt{I think we can delete these: including Demographic and Health Surveys (DHS), Multiple Indicator Cluster Surveys (MICS), and other nationally representative surveys} between 2004 to 2015, that more than 200 million women and girls have undergone female genital cutting (FGC), mostly in Africa and the Middle East, and among them, 44 million are girls below age 15.  It was also predicted that another 15 million girls and women are at risk by 2020  \cite{AdnrLesc16, UNIC16}.  Progress of intervention is hindered because of the complicated history \cite{BergDeni12, Cami16} and of not keeping up with the population growth \cite{KhosBane17, UNIC16}.  Following Tostan \cite{Tost15}, we used cutting instead of circumcision without demising or excusing the negative impact of the practice while recognizing a sense of self-awareness in making decision about FGC \cite{KhahBark09, JohnEsse10, Meye00, PariSaru18, Shel01, Tost15}. \cfonly{less cites}

FGC is embodied with multiple approaches from cultural and religious identity in one end and public health and human rights concerns on the other} \cite{AhmeKare18, BergDeni13a, Boyl02, BoylMcMo02, Grue01, KhosBane17, KimaShell18, McCh15, SchuLien13, WHO12}. \cfonly{too many cites}.  Understanding reasons and values people attached to FGC is essential to comprehend the persistence of the practice \cite{Bicc10, CislHeis18, Mack96} in order to negotiate, intervene and reduce possible harmful intervention \cite{Cami15} \cfonly {check cite}.  Social norm, a form of values driving behavioural patterns which are self-enforcing within a group \cite{Youn15}; it can refer to an average outcome or a common practice \cite{MillPrin16}.   Social norms is widely applied in understanding public health behaviours \cite{Ajze91, Ajze02, CislHeis18a, MillPrin16, MollRima10, RimaLapi15}, provides a crucial venue in negotiating sustainable changes of FGC practice \cite{Bicc10, BiccMari15, BoylCorl010, DuncWand11, Drol11, EffeVogt15, Hayf05, HayfTrin11, Grue05, Hodg11,KandNwak09, Mack96, Mack00, MackLeJe08, OdukAfol17, RimaLapi15, Youn02, Youn11, UNIC10, UNIC13} \cfonly{less}.

FGC values and norms tended to be deeply internalized and morally embraced \cite{SchuLien13}.  Social convention theory, a leading theory (e.g., \cite{BoylMcMo02, BoylCorl10, FreyJohn07, FrieMahm13, Hayf05, KandMwek09, Mack96, Mack06, ReigGonz14, YirgKass12}) utilizing normative behavior in FGC research \cite{Hayf05, ShelWand11} \cfonly{more} proposed that FGC was a marriageability convention and extending to, latter, a social norm, such as religious obligation, adolescent rite of passage, and female honour and modesty to control marriage fidelity and social prestige \cite{Mack00, MackLeJe08}.   FGC was furthered deemed as a form of social capital, a value respected by women for inclusion within their social groups \cite{ShelWand11}. The social convention theory regards FGC a social behaviour interdependent among and coordinated by members in their social network \cite{Mack00, MackLeJe08, ShelWand11}.  Social expectation (i.e., what other people do or what other people believe one should do) was strongly correlated with FGC practice \cite{BiccMari15}.  Basically, when the norms within the communities are strong, individuals tend to self-enforce community norms \cite{Ajze02, Hayf05, KandNwak09, KandShel19, Mack96, Mack06, MackLeJe08, ThomMadd92} \cfonly{add \cite{Bicc15}}.

\cfonly{We believe this is the first FGC study using attitudes to model FGC intention by utilizing FGC norm (community level or FGC prevalence and intention)}

@@

% “A daughter’s adjusted hazard of FGMC was lower if she had an uncut mother who disfavored FGMC, lived in a community that was more opposed to FGMC, and lived in a more ethnically diverse community. Unexpectedly, a daughter’s adjusted FGMC hazard was higher if she lived in a community with more extrafamilial opportunities for women. “ \cite{GrosHayf19}
% education:  \cite{DalaLawo10, IliyAbub12, KandNwak09, KarmKand11, PashPonn16, VanMeek1}; also \cite{Hayf06} also showed that group education was not a clearly related to fgc plan like individual eduction did.
